---
title: "TimeTable"
description: |
  Check your instructor timetable.  
author: 
  - name: "Kamarul Ariffin Mansor"
    url: https://my.linkedin.com/in/kamarul-ariffin-mansor-254b9ba7/
    affiliation: Universiti Teknologi MARA
    affiliation_url: https://kedah.uitm.edu.my/v2/index.php
date: 3-19-2021
output: 
  distill::distill_article:
    self_contained: true
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html
```


### Lecturer's Timetable  

#### 20212 (click on the program name to display content)  

<details>
```{r}
library(stringr)
library(bsselectR)

tt_plots <- paste0(list.files("images/tt", full.names = TRUE))
names(tt_plots) <- str_replace_all(tt_plots, 
                                      c("\\.jpg" = "", 
                                        "images/tt/" = ""))

bsselect(tt_plots, type = "img", selected = "ab-razak", 
         live_search = TRUE, show_tick = TRUE)
```
</details>

***  

### Class Representatives  

#### Session - 20214 (click on the program name to display content)  

<details><summary>AC110</summary>
  <center><embed src="./files/20214/wakil_kelas/AC110.pdf" type="application/pdf" width="100%" height="660px" /><p>If you can't view the pdf file, click on the file's link - <a href="./files/20214/wakil_kelas/AC110.pdf">Download PDF!</a></p></center>
</details>

<details><summary>AM110 & AM228</summary>
  <center><embed src="./files/20214/wakil_kelas/AM110 & AM228.pdf" type="application/pdf" width="100%" height="660px" /><p>If you can't view the pdf file, click on the file's link - <a href="./files/20214/wakil_kelas/AM110 & AM228.pdf">Download PDF!</a></p></center>
</details>

<details><summary>CS110</summary>
  <center><embed src="./files/20214/wakil_kelas/CS110.pdf" type="application/pdf" width="100%" height="660px" /><p>If you can't view the pdf file, click on the file's link - <a href="./files/20214/wakil_kelas/CS110.pdf">Download PDF!</a></p></center>
</details>

#### Session - 20212 (click on the program name to display content)  

<details>
```{r}
library(stringr)
library(bsselectR)

wakil_plots <- paste0(list.files("images/wakil", full.names = TRUE))
names(wakil_plots) <- str_replace_all(wakil_plots, 
                                      c("\\.jpg" = "", 
                                        "images/wakil/" = ""))

bsselect(wakil_plots, type = "img", selected = "AC110", 
         live_search = TRUE, show_tick = TRUE)
```
</details>